### 2025-05-02 docs/Homeownership_BankOfMomAndDad.tex
More polish

\section{Introduction}
Housing is the largest asset in U.S. household portfolios. While homeownership is seen as central to the ``American Dream'' \citep{goodman2018homeownership}, households face different barriers to ownership. Between 2009 and 2016, around 30\% of American first-time homebuyers received direct parental assistance for their down payment, with such assistance averaging \$48,000 per receiving household\textcolor{red}{Check numbers}.\footnote{All data from the Survey of Household Economic Decisionmaking and the Panel Study of Income Dynamics (see Section \ref{sec:data}).} This assistance highlights disparities in access, as only those with sufficiently wealthy parents can expect substantial transfers.

@@

I made several simplifying assumptions to keep the model tractable. Adding richer housing dynamics and equilibrium effects would allow one to study other interesting questions, such as the extent to which transfers contribute to house price growth. My model omits a feedback loop, in which transfers raise demand and, thus, house prices, boosting the wealth of homeowning parents and, thus, higher transfers, and so on. Another potential extension could examine whether illiquidity may reduce the commitment problem in the family. Additionally, my preferences-for-illiquidity results have implications for the literature on high-MPC households \citep[see e.g.,][]{kaplan2022marginal}. In particular, we are likely overestimating the average MPC of liquidity-constrained households with wealthy parents, since these households use parental transfers to smooth shocks. For example, following a negative shock, consumption may fall less due to transfers, while for positive shocks, consumption may rise less as parents reduce transfers.

>>>>

\section{Introduction}
Housing is the largest asset in U.S. household portfolios. While homeownership is seen as central to the ``American Dream'' \citep{goodman2018homeownership}, households face different barriers to ownership. Between 2009 and 2016, around 30\% of American first-time homebuyers received direct parental assistance for their down payment.\footnote{Source: Survey of Household Economic Decisionmaking (see Section \ref{sec:data}).} This assistance highlights disparities in access, as only those with sufficiently wealthy parents can expect substantial transfers.

@@

I made several simplifying assumptions to keep the model tractable. Adding richer housing dynamics and equilibrium effects would allow analysis of other interesting questions, such as the extent to which transfers contribute to house price growth. My model omits a feedback loop, in which transfers raise housing demand, which leads to higher prices and thus increasing the wealth of homeowning parents and enabling further transfers. Another potential extension could examine whether illiquidity reduces the commitment problem in the family. Additionally, my results on preferences for illiquidity have implications for the literature on high-MPC households \citep[see e.g.,][]{kaplan2022marginal}. In particular, by ignoring transfers, existing work overestimates the average MPC of liquidity-constrained households, some of whom rely on parental transfers to smooth shocks.
